%-------------------------
% Resume in Latex
% Author : Navaneet R Rao
% Based on: https://github.com/sb2nov/resume
% License : MIT
%------------------------


\documentclass[letterpaper,16pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{setspace}

\input{glyphtounicode}

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}


% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}

% serif
\usepackage{charter}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\bfseries\scshape\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
% -------------------- START OF DOCUMENT --------------------
\begin{document}
% -------------------- HEADING --------------------

    \begin{center}
        \textbf{\Huge \scshape Navaneet R Rao}
        \\ 
        
        % \faIcon{code}
        % \href{https://navaneet-rao.github.io/portfolio-website/}
        % {\underline{/portfolio-website}} 
            
        \vspace{8pt}
        
        {\large 
            {
                \faIcon{github}
                    \href{https://github.com/navaneet-rao}
                {\color{Aquamarine}\underline{github.com/navaneet-rao}} \ \ \ \  
                \faIcon{linkedin}
                    \href{https://www.linkedin.com/in/navaneet-r-rao}
                {\color{Aquamarine}\underline{linkedin.com/in/navaneet-r-rao}} \ \ \ \ 
                \faIcon{envelope}
                    \href{mailto:navaneet517@gmail.com}
                {\color{Aquamarine}\underline{navaneet517@gmaill.com}}
            }
        
        }
    \end{center}

%----------- EDUCATION -----------------
\section{Education }
  \resumeSubHeadingListStart
    \resumeSubheading
      {Jyothy Institute of Technology - VTU}{Bengaluru, Karnataka}
      {Bachelor of Engineering (B.E) in Computer Science (3rd Year) -- \textbf{7.55 GPA}}{Dec. 2021 -- Present}
  \resumeSubHeadingListEnd
  
%----------- PROFESSIONAL EXPERIENCE -----------------
\section{Professional Experience }
 \resumeSubHeadingListStart
 
      \resumeSubheading
      {Enterprise Building Training Solutions (EBTS)}{Bengaluru}
      {Cyber security Essentials Intern}{May. 2022}
    \resumeItemListStart
        \resumeItem
          {Applied practical skills, identifying vulnerabilities and proposing effective mitigation strategies.}
        \resumeItem
          {Collaborated with Cyber security professionals, gaining valuable insights into practical aspects.}
        \resumeItem
          {Experienced in \textbf{CTFs}, Honeypots, firewalls, and more.}
        \resumeItem
          {Implemented firewall rules using \textbf{pf Sense} and increasing network security and seamless traffic management by \textbf{35\%}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Red Hat -- \href{https://rhtapps.redhat.com/verify?certId=230-264-087}{\color{Aquamarine}\underline{Certificate}}}{Bengaluru}
      {Red Hat internship training}{Oct. 2022 - Nov. 2022}
      \resumeItemListStart
        \resumeItem
          {Enhanced system security, managed essential networking, proficiently handled user and group administration, executed seamless deployment and ongoing system maintenance, adeptly addressed troubleshooting challenges.}
        \resumeItem
          {Orchestrated containerized systemd services for an httpd/CentOS image on the Red Hat Enterprise Linux (RHEL) platform.}
        \resumeItem
          {Implemented CI/CD through \textbf{Open Shift} with \textbf{GitHub} for Version control for a react-based website }
        \resumeItem
          {The specialized training contributed to the successful completion of the \textbf{EX200} Red Hat Certified System Administrator exam with a score of \textbf{87\%} }
      \resumeItemListEnd

  \resumeSubHeadingListEnd    

%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{Network Security Analyst - NMAP} $|$ \footnotesize\emph{Kali Linux, NMAP, Wireshark}}{May. 2022}
        \resumeItemListStart
            \resumeItem{Utilized key tools, including \textbf{NMAP} and \textbf{Wireshark}, to identify and evaluate potential vulnerabilities within the 3 different domains}
            \resumeItem{Conducted targeted scans on \textbf{70\%} of three \textbf{FQDNs}, successfully identifying vulnerabilities in \textbf{10\%} of the scanned domains.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{Data Restoration from a PCap File} $|$ \footnotesize\emph{Kali Linux, Wireshark, HxD}}{Jun. 2023}
        \resumeItemListStart
            \resumeItem{Applied Wireshark for thorough analysis and interpretation of a \textbf{PCap} file, extracting key insights into \textbf{Network Communication}}
            \resumeItem{Proficiently used \textbf{HxD} for precise data restoration, successfully recovering \textbf{95\%} of data with proficiency in recognizing and interpreting various  \textbf{file signatures} during the process. }
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{Real Time Automated Notification} $|$ \footnotesize\emph{Windows, Powershell, NTFY}}{Sep. 2023}
        \resumeItemListStart
            \resumeItem{Developed an \textbf{automated push notification} system using the NTFY library and PowerShell scripting to enhance \textbf{real-time} communication within a Windows environment.}
            \resumeItem{This PowerShell script continuously monitors the battery status of a system, sending notifications using NTFY and executing an additional script when transitioning between battery and plugged-in states.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{Me2Chat - Real-time Chat App} $|$ \footnotesize\emph{React Native, Expo, Typescript, Tailwind CSS, Firebase}}{Dec. 2023}
        \resumeItemListStart
            \resumeItem{Developed a real-time chat application using React Native, Expo, Typescript, Tailwind CSS, and Firebase.}
            \resumeItem{Implemented user authentication, allowing users to securely sign in and register.}
            \resumeItem{Utilized Firebase \textbf{Realtime} Database for efficient and synchronized data updates in real-time.}
        \resumeItemListEnd
     
    \resumeSubHeadingListEnd


%--------------PROGRAMMING SKILLS-------------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, HTML, CSS, C, C++, C\#, Java, PowerShell, LaTeX}
     \hfill \\
     \textbf{Libraries/Frameworks}{: ReactJS, React Native, NodeJS, TaildwindCSS, Boorstrap, Flask, Computer Vision, Jupyter Notebook}
     \hfill \\
     \textbf{Databases}{: MySQL, MongoDB, Firebase}
     \hfill \\
     \textbf{Tools}{: VSCode, Git, GCP, VMWare, VBox, Docker, Pod man, open shift, NMAP, Wireshark, Arduino, MS Office}
   }
 \resumeSubHeadingListEnd
%--------------CERTIFICATIONS-------------------
\section{Certifications}
 \resumeSubHeadingListStart
   \item{
     \textbf{Front-End Web UI Frameworks and Tools: Bootstrap 4, }{Coursera -- \href{https://coursera.org/share/6f277b468374e3dbe6a26c67811db539}{\color{Aquamarine}\underline{Certificate}}}
     \hfill \\
     \textbf{Introduction to Cybersecurity Tools \& Cyber Attacks, }{Coursera -- \href{https://coursera.org/share/317c6874e71c67cfde693de6e5de7e49}{\color{Aquamarine}\underline{Certificate}}}
     \hfill \\
     \textbf{Cybersecurity Roles, Processes \& Operating System Security, }{Coursera -- \href{https://coursera.org/share/2ab125b6a50b05a2ed5eb454cce95afd}{\color{Aquamarine}\underline{Certificate}}}
     \hfill \\
     \textbf{Nmap for Ethical Hackers - The Ultimate Hands-On Course, }{Udemy -- 
     \href{https://www.udemy.com/certificate/UC-bd741301-70d9-4a30-a11e-26f92aa1c287/}{\color{Aquamarine}\underline{Certificate}}}
     \hfill \\
     \textbf{EX200 Red Hat Certified System Administrator, }{Red Hat -- \href{https://rhtapps.redhat.com/verify?certId=230-264-087}{\color{Aquamarine}\underline{Certificate}}}
     \hfill \\
     \textbf{Google Cloud Fundamentals: Core Infrastructure, }{Google Cloud Skills Boost -- \href{https://www.cloudskillsboost.google/public_profiles/bd9c5896-4d7c-44d8-aa79-295b8944bf04/badges/4323872}{\color{Aquamarine}\underline{Certificate}}}
     \hfill \\
     \textbf{Essential Google Cloud Infrastructure: Foundation, }{Google Cloud Skills Boost -- \href{https://www.cloudskillsboost.google/public_profiles/bd9c5896-4d7c-44d8-aa79-295b8944bf04/badges/4760001?utm_medium=social&utm_source=linkedin&utm_campaign=ql-social-share}{\color{Aquamarine}\underline{Certificate}}}
   }
 \resumeSubHeadingListEnd
%----------- END OF DOCUMENT -----------------
\end{document}
